Covariate analysis of ROSMAP RNASeq

### 2016-01-08 code/Rmd/ROSMAP_RNASeq.Rmd
Minor bug fix

knit2synapse::knitToFolderEntity(file = "./ROSMAP_RNASeq.Rmd",
                                 parentId ="syn5570291",
                                 entityName = 'ROSMAP RNASeq')
```

@@

# Query biomart
Ensemble2HGNC <- getBM(attributes = c("ensembl_gene_id", "hgnc_symbol"),
                       filters = "ensembl_gene_id", values = RESIDUAL.GENE_EXPRESSION$ensembl_gene_id,
                       mart = mart)
RESIDUAL.GENE_EXPRESSION <- left_join(RESIDUAL.GENE_EXPRESSION, Ensemble2HGNC) %>%
  dplyr::select(ensembl_gene_id, hgnc_symbol, one_of(rownames(COVARIATES)))
```
### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE}
# Code
CODE <- Folder(name = "Differential Expression Analysis ROSMAP RNASeq (Based on cogdx)", parentId = parentId)
CODE <- synStore(CODE)

@@

# Store covariates
write.table(RESIDUAL.GENE_EXPRESSION, file = 'expression.tsv', sep = '\t', row.names=F, quote=F)
EXP_OBJ = File('expression.tsv', name = 'FPKM Normalised Adjusted Residual Expression (cogdx added)', parentId = CODE$properties$id)
EXP_OBJ = synStore(EXPRP_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                   executed = thisFile, activityDescription = activityDescription)
```
|  *Results*            |  *SynapseID*                    |
|  -------              |   ---------                     |
|  Covariates           |  `r COV_OBJ$properties$id`      |
|  Residual Expression  |  `r EXP_OBJ$properties$id`      |

>>>>

knit2synapse::knitToFolderEntity(file = "./ROSMAP_RNASeq.Rmd",
                                 parentId ="syn5570291",
                                 entityName = 'ROSMAP RNASeq (Based on cogdx)')
```

@@

# Query biomart
Ensemble2HGNC <- getBM(attributes = c("ensembl_gene_id", "hgnc_symbol"),
                       filters = "ensembl_gene_id", values = RESIDUAL.GENE_EXPRESSION$ensembl_gene_id,
                       mart = mart)
RESIDUAL.GENE_EXPRESSION <- left_join(RESIDUAL.GENE_EXPRESSION, Ensemble2HGNC) %>%
  dplyr::select(ensembl_gene_id, hgnc_symbol, one_of(rownames(COVARIATES)))
```
### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Code
CODE <- Folder(name = "ROSMAP RNASeq (Based on cogdx)", parentId = parentId)
CODE <- synStore(CODE)

@@

# Store covariates
write.table(RESIDUAL.GENE_EXPRESSION, file = 'expression.tsv', sep = '\t', row.names=F, quote=F)
EXP_OBJ = File('expression.tsv', name = 'FPKM Normalised Adjusted Residual Expression (cogdx added)', parentId = CODE$properties$id)
EXP_OBJ = synStore(EXP_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                   executed = thisFile, activityDescription = activityDescription)
```
|  *Results*            |  *SynapseID*                    |
|  -------              |   ---------                     |
|  Covariates           |  `r COV_OBJ$properties$id`      |
|  Residual Expression  |  `r EXP_OBJ$properties$id`      |
